The cardinality-constrained college application problem: The nestedness property and implications for student welfare

### 2022-07-21 paper_alma/abstract.tex
line edits, remove unreferenced equation numbers

This paper considers a novel portfolio optimization problem called the college application problem. We show that the objective function is a nondecreasing submodular set function and provide a quadratic-time solution algorithm. We discuss the properties of the optimal solution and their implications for student welfare.

>>>>

This paper considers a novel portfolio optimization problem called the college application
problem. We show that the objective function is a nondecreasing submodular set function
and provide a quadratic-time solution algorithm for its maximization over a cardinality
constraint. An analysis of the structure of the optimal portfolios suggests a rational basis
for systematic differences in the application styles of low- and high-income students observed
in regression studies. Our results also suggest that behavioral nudges (such as application
fee waivers) designed to encourage low-income students to apply to more colleges have yielded
underwhelming results because they target students with relatively low shadow costs.
